Radio Crickets: Chirping Jets from Black Hole Binaries Entering their Gravitational Wave Inspiral

### 2015-07-08 Paper/paper.tex
Change from ApJ to MNRAS format

\documentclass[iop]{emulateapj}
\bibliographystyle{apj}
\usepackage{amsmath} 
\usepackage{aas_macros,amssymb}
\usepackage{natbib,graphicx,layouts}
\usepackage{color,hyperref}
\usepackage{bm}
\definecolor{linkcolor}{rgb}{0,0,0.5}
\definecolor{notecolor}{rgb}{0.8,0,0}
\hypersetup{colorlinks=true,linkcolor=linkcolor,citecolor=linkcolor,
  filecolor=linkcolor,urlcolor=linkcolor}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing}

\shorttitle{Chirping Jets from Black Hole Binaries}
\shortauthors{Kulkarni et al.}

\begin{document}

\title{Radio Crickets: Chirping Jets from Black Hole Binaries Entering
  their Gravitational Wave Inspiral} \author{Girish
  Kulkarni\altaffilmark{1} and Abraham Loeb\altaffilmark{2}}
\altaffiltext{1}{Institute of Astronomy and Kavli Institute of
  Cosmology, University of Cambridge, Madingley Road, Cambridge CB3
  0HA, UK; \email{kulkarni@ast.cam.ac.uk}} \altaffiltext{2}{Institute
  for Theory \& Computation, Harvard University, 60 Garden Street,
  Cambridge, MA 02138, USA; \email{aloeb@cfa.harvard.edu}}

\begin{abstract}
We study a novel electromagnetic signature of supermassive black hole
binaries whose inspiral stars being dominated by gravitational wave
(GW) emission. Combined GW and electromagnetic observations of compact
binary mergers would allow to use them as standard sirens for
cosmology and a testing ground of general relativity.  If one of the
binary members produces a radio jet, the helical chirping morphology
of the jet can be used to infer the binary parameters.  For binaries
with mass $10^7$--$10^{10}$ M$_\odot$ at redshifts $z<0.5$, the jet
precesses along a biconical surface due to the binary's orbital
motion.  When the binary enters the GW phase of its evolution, the
opening angle widens, the jet exhibits milliarcsecond scale wiggles
and the conical surface of jet precession is twisted due to the
superluminal motion.  Monitoring these features in current and
archival data will place a lower limit on sources that could be
detected by eLISA and Pulsar Timing Arrays.  In the future,
microarcsecond interferometry with the Square Kilometer Array will
increase the potential usefulness of this technique.
\end{abstract}

\keywords{BHs}

@@

\bibliography{refs}
\end{document}

>>>>

\documentclass[a4paper,fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
%% \usepackage{newtxtext,newtxmath}

% Depending on your LaTeX fonts installation, you might get better results with one of these:
%% \usepackage{mathptmx}
%% \usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathmorphing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

\title[Chirping Jets from Black Hole Binaries]{Radio Crickets:
  Chirping Jets from Black Hole Binaries Entering their Gravitational
  Wave Inspiral}

\author[Kulkarni and Loeb]{
Girish Kulkarni,$^{1}$\thanks{E-mail: kulkarni@ast.cam.ac.uk}
and Abraham Loeb$^{2}$\thanks{E-mail: aloeb@cfa.harvard.edu}
\\
$^{1}$Institute of Astronomy and Kavli
  Institute of Cosmology, University of Cambridge, Madingley Road,
  Cambridge CB3 0HA, UK\\ 
$^{2}$Institute for Theory \& Computation,
  Harvard University, 60 Garden Street, Cambridge, MA 02138, USA\\ 
}

% These dates will be filled out by the publisher
\date{Accepted ---. Received ---; in original form ---}

% Enter the current year, for the copyright statements etc.
\pubyear{2015}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
  We study a novel electromagnetic signature of supermassive black
  hole binaries whose inspiral stars being dominated by gravitational
  wave (GW) emission. Combined GW and electromagnetic observations of
  compact binary mergers would allow to use them as standard sirens
  for cosmology and a testing ground of general relativity.  If one of
  the binary members produces a radio jet, the helical chirping
  morphology of the jet can be used to infer the binary parameters.
  For binaries with mass $10^7$--$10^{10}$ M$_\odot$ at redshifts
  $z<0.5$, the jet precesses along a biconical surface due to the
  binary's orbital motion.  When the binary enters the GW phase of its
  evolution, the opening angle widens, the jet exhibits milliarcsecond
  scale wiggles and the conical surface of jet precession is twisted
  due to the superluminal motion.  Monitoring these features in
  current and archival data will place a lower limit on sources that
  could be detected by eLISA and Pulsar Timing Arrays.  In the future,
  microarcsecond interferometry with the Square Kilometer Array will
  increase the potential usefulness of this technique.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
keyword1 -- keyword2 -- keyword3
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

@@

\bibliographystyle{mnras}
\bibliography{refs} % if your bibtex file is called example.bib

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

### 2015-07-08 Paper/scratch.tex
Change from ApJ to MNRAS format

>>>>

Normally the next section describes the techniques the authors used.
It is frequently split into subsections, such as Section~\ref{sec:maths} below.

\subsection{Maths}
\label{sec:maths} % used for referring to this section from elsewhere

Simple mathematics can be inserted into the flow of the text e.g. $2\times3=6$
or $v=220$\,km\,s$^{-1}$, but more complicated expressions should be entered
as a numbered equation:

\begin{equation}
    x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}.
	\label{eq:quadratic}
\end{equation}

Refer back to them as e.g. equation~(\ref{eq:quadratic}).

\subsection{Figures and tables}

Figures and tables should be placed at logical positions in the text. Don't
worry about the exact layout, which will be handled by the publishers.

Figures are referred to as e.g. Fig.~\ref{fig:example_figure}, and tables as
e.g. Table~\ref{tab:example_table}.

% Example figure
\begin{figure}
	% To include a figure from a file named example.*
	% Allowable file formats are eps or ps if compiling using latex
	% or pdf, png, jpg if compiling using pdflatex
	\includegraphics[width=\columnwidth]{example}
    \caption{This is an example figure. Captions appear below each figure.
	Give enough detail for the reader to understand what they're looking at,
	but leave detailed discussion to the main body of the text.}
    \label{fig:example_figure}
\end{figure}

% Example table
\begin{table}
	\centering
	\caption{This is an example table. Captions appear above each table.
	Remember to define the quantities, symbols and units used.}
	\label{tab:example_table}
	\begin{tabular}{lccr} % four columns, alignment for each
		\hline
		A & B & C & D\\
		\hline
		1 & 2 & 3 & 4\\
		2 & 4 & 6 & 8\\
		3 & 5 & 7 & 9\\
		\hline
	\end{tabular}
\end{table}
